mixchar

### 2018-08-07 README.Rmd
correct pkgdown and add text to readme
update headers and add website links

## Why deconvolution?

@@

## Installation

@@

## Basic use

@@

You can see the full worked example in the vignette, which you can access on the or in R:
```{r}
vignette('mixchar')
```

@@

## Acknowledgements
Thank you to Nick Tierney for valuable feedback during development. Thanks to the Holsworth Wildlife Reseach Endowment & The Ecological Society of Australia for support on this project.

>>>>

# Why deconvolution?

@@

# Installation

@@

# Basic use

@@

You can see the full worked example in the vignette, which you can access on the [website](http://smwindecker.github.io/mixchar) or in R:
```{r}
vignette('mixchar')
```

A detailed discussion of the methodology is also on the [website](http://smwindecker.github.io/Background).

@@

# Acknowledgements
Thank you to Nick Tierney for valuable feedback during development. Thanks to the Holsworth Wildlife Reseach Endowment & The Ecological Society of Australia for support on this project.
